Bandit Multiclass Linear Classification: \\ Efficient Algorithms for the Separable Case

### 2019-01-23 ICML-submission/algorithm-for-strongly-linearly-separable-data.tex
Fixes

Algorithm~\ref{algorithm:algorithm-for-strongly-linearly-separable-examples} can
be extended to nonlinear classification using \emph{positive definite kernels}
(or \emph{kernels}, for short), which are functions of the form $k: X \times X
\to \R$ for some set $X$ such that the matrix
$\left(k(x_i,x_j)\right)_{i,j=1}^m$ is a symmetric positive semidefinite for any
positive integer $m$ and $x_1, x_2, \dots, x_m \in X$ \citep[Definition
2.5]{Scholkopf-Smola-2002}.\footnote{Every kernel has an associated feature map
$\phi:X \to V$ for some inner product space $(V,\ip{\cdot}{\cdot})$ such that
$k(x,x') = \ip{\phi(x)}{\phi(x')}$.} As opposed to explicitly maintaining the
weight vector for each class, the algorithm maintains the set of example-scalar
pairs corresponding to the updates of the non-kernelized algorithm. As a direct
consequence of
Theorem~\ref{theorem:strongly-separable-examples-mistake-upper-bound} we get a
mistake bound for the kernelized algorithm.

>>>>

Algorithm~\ref{algorithm:algorithm-for-strongly-linearly-separable-examples} can
be extended to nonlinear classification using \emph{positive definite kernels}
(or \emph{kernels}, for short), which are functions of the form $k: X \times X
\to \R$ for some set $X$ such that the matrix
$\left(k(x_i,x_j)\right)_{i,j=1}^m$ is a symmetric positive semidefinite for any
positive integer $m$ and $x_1, x_2, \dots, x_m \in X$ \citep[Definition
2.5]{Scholkopf-Smola-2002}.\footnote{For every kernel there exists an associated feature map
$\phi:X \to V$ into some inner product space $(V,\ip{\cdot}{\cdot})$ such that
$k(x,x') = \ip{\phi(x)}{\phi(x')}$.} As opposed to explicitly maintaining the
weight vector for each class, the algorithm maintains the set of example-scalar
pairs corresponding to the updates of the non-kernelized algorithm. As a direct
consequence of
Theorem~\ref{theorem:strongly-separable-examples-mistake-upper-bound} we get a
mistake bound for the kernelized algorithm.
